---
title: "Developing Data products - Exercise 2"
author: "Carlos Ochoa"
date: "20th June 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise

Create a web page using R Markdown that features a map created with Leaflet.
Host your webpage on either GitHub Pages, RPubs, or NeoCities.
Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

## Data

We have uploaded the location and population of all the cities in Spain. After filtering cities with less of 10,000 habitants, we have presented each city in the map, with a cicle proportional to the population and a color corresponding to one of the 18 main regions of Spain.


```{r map, echo=FALSE, warning=FALSE}
library(leaflet)

geoloc <- read.csv("CitiesGeoloc.csv",sep=";", encoding = "UTF-8", colClasses = c(NA,NA,NA,"numeric","numeric","numeric","numeric","numeric","numeric"))

names(geoloc) <- c("region","province","city","lat","lng","alt","population","male","female")
geoloc<-geoloc[geoloc$population>10000,]

pal <- colorNumeric(palette = palette(), domain = as.numeric(geoloc$region))
map<- geoloc %>% 
  leaflet() %>%
  addTiles() %>% 
  addCircleMarkers (
    weight = 1, 
    radius=sqrt(geoloc$population)/50, 
    fillColor =pal(as.numeric(geoloc$region))) %>%
  addLegend(
    "bottomleft", 
    color=pal(1:18),
    labels = levels(geoloc$region),
    title = "Regions",
    opacity = 1)

map

```

